New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2022-09-30 paper/appendix.Rmd
navigation for slice center in appendix and removed small section from main paper

>>>>

# Slice center guide

The slice center, $c$, from Equation 1 in the main paper, is a point in the $p$-dimensional space. By default it is placed in the center of the data (plot A). Moving this along a variable axis moves the slice outwards from the center of the data (plots B, C).

```{r anchornav, fig.width=10, fig.height=3, out.width="100%", fig.cap="Visual guide for the slice center. Variable axes are displayed in polar coordinates, where the center corresponds to minimum value and outer end corresponds to maximum value. The position of the center corresponds to the dark polygon. If the center is at the center of the data, this will be displayed as a regular polygon (A), and plots B, C show it's position when moving the center along one axis."}
par(pty="s", mfrow=c(1,3))
plot(c(-1, 1), c(-1, 1), type="n", axes=FALSE, xlab = "", ylab = "", main="A. data center")
anchor = data.frame(matrix(rep(0.5, 6), ncol=6))
tourr:::draw_slice_center(
   anchor, 
   rng = matrix(rep(c(0,1), 6), ncol=6, byrow=FALSE),
   limits = 1, anchor_nav = "center")
plot(c(-1, 1), c(-1, 1), type="n", axes=FALSE, xlab = "", ylab = "", main="B. center moved towards max value of X3")
anchor[3] <- 0.75
tourr:::draw_slice_center(
   anchor, 
   rng = matrix(rep(c(0,1), 6), ncol=6, byrow=FALSE),
   limits = 1, anchor_nav = "center")
plot(c(-1, 1), c(-1, 1), type="n", axes=FALSE, xlab = "", ylab = "", main="C. center moved towards min value of X3")
anchor[3] <- 0.25
tourr:::draw_slice_center(
   anchor, 
   rng = matrix(rep(c(0,1), 6), ncol=6, byrow=FALSE),
   limits = 1, anchor_nav = "center")
```

### 2022-09-30 paper/appendix.tex
navigation for slice center in appendix and removed small section from main paper

>>>>

\hypertarget{slice-center-guide}{%
\section{Slice center guide}\label{slice-center-guide}}

The slice center, \(c\), from Equation 1 in the main paper, is a point
in the \(p\)-dimensional space. By default it is placed in the center of
the data (plot A). Moving this along a variable axis moves the slice
outwards from the center of the data (plots B, C).

\begin{figure}
\includegraphics[width=1\linewidth]{appendix_files/figure-latex/anchornav-1} \caption{Visual guide for the slice center. Variable axes are displayed in polar coordinates, where the center corresponds to minimum value and outer end corresponds to maximum value. The position of the center corresponds to the dark polygon. If the center is at the center of the data, this will be displayed as a regular polygon (A), and plots B, C show it's position when moving the center along one axis.}\label{fig:anchornav}
\end{figure}

### 2022-09-30 paper/paper.Rmd
navigation for slice center in appendix and removed small section from main paper

One might implement such an interactive interface via R Shiny, but in particular the tracking of the mouse position in small increments might pose a challenge. Here we found the dynamic graphics interface from Mathematica to be especially useful. In the following we first describe the relevant Mathematica functionalities and how they were used in the implementation, followed by a brief sketch of how the new approaches are implemented in the `tourr` package.

@@

The R package tourr [@tourr] provides numerous types of tours. An additional function, `radial_tour()` has been constructed that will generate a sequence of projections that will decrease the coordinates for $V_m$ to $\boldsymbol{0}$ and back to the original values. It is applicable for any projection dimension, $d$. Changing slice center manually can be accomplished with the new function, `manual_slice()`. This changes the value of the center point ($\mathbf{c}$) of the slice, along a selected variable axis. It slices from the center of the data out to one side, back to the center, out to the opposite side, and then back to the center.

## Desirable interactivity

Potential adjustments for future work include a better visualization of the current center point, potentially with interactive graphics to move the slice, similarly to how the manual tour was implemented here. An alternative would be a step-wise shift of the slice towards the new center point to get a better understanding of the distribution along the selected direction.

>>>>

One might implement such an interactive interface via R Shiny, but in particular the tracking of the mouse position in small increments might pose a challenge. Here we found the dynamic graphics interface from Mathematica to be especially useful. In the following we first describe the relevant Mathematica functionalities and how they were used in the implementation, followed by a brief sketch of how the new approaches are implemented in the `tourr` package. There is hope that better interactivity will be available for R soon, which might allow for implementation of the techniques developed in Mathematica.

@@

The R package tourr [@tourr] provides numerous types of tours. An additional function, `radial_tour()` has been constructed that will generate a sequence of projections that will decrease the coordinates for $V_m$ to $\boldsymbol{0}$ and back to the original values. It is applicable for any projection dimension, $d$. Changing slice center manually can be accomplished with the new function, `manual_slice()`. This changes the value of the center point ($\mathbf{c}$) of the slice, along a selected variable axis. It slices from the center of the data out to one side, back to the center, out to the opposite side, and then back to the center. The appendix contains a discussion of a possible visual guide for the slice center location.

<!--
I don't think the paper gains anything by having this section.
## Desirable interactivity

Potential adjustments for future work include a better visualization of the current center point, potentially with interactive graphics to move the slice, similarly to how the manual tour was implemented here. An alternative would be a step-wise shift of the slice towards the new center point to get a better understanding of the distribution along the selected direction.
-->

### 2022-09-30 paper/paper.tex
navigation for slice center in appendix and removed small section from main paper

One might implement such an interactive interface via R Shiny, but in
particular the tracking of the mouse position in small increments might
pose a challenge. Here we found the dynamic graphics interface from
Mathematica to be especially useful. In the following we first describe
the relevant Mathematica functionalities and how they were used in the
implementation, followed by a brief sketch of how the new approaches are
implemented in the \texttt{tourr} package.

@@

The R package tourr \citep{tourr} provides numerous types of tours. An
additional function, \texttt{radial\_tour()} has been constructed that
will generate a sequence of projections that will decrease the
coordinates for \(V_m\) to \(\boldsymbol{0}\) and back to the original
values. It is applicable for any projection dimension, \(d\). Changing
slice center manually can be accomplished with the new function,
\texttt{manual\_slice()}. This changes the value of the center point
(\(\mathbf{c}\)) of the slice, along a selected variable axis. It slices
from the center of the data out to one side, back to the center, out to
the opposite side, and then back to the center.

\hypertarget{desirable-interactivity}{%
\subsection{Desirable interactivity}\label{desirable-interactivity}}

Potential adjustments for future work include a better visualization of
the current center point, potentially with interactive graphics to move
the slice, similarly to how the manual tour was implemented here. An
alternative would be a step-wise shift of the slice towards the new
center point to get a better understanding of the distribution along the
selected direction.

>>>>

One might implement such an interactive interface via R Shiny, but in
particular the tracking of the mouse position in small increments might
pose a challenge. Here we found the dynamic graphics interface from
Mathematica to be especially useful. In the following we first describe
the relevant Mathematica functionalities and how they were used in the
implementation, followed by a brief sketch of how the new approaches are
implemented in the \texttt{tourr} package. There is hope that better
interactivity will be available for R soon, which might allow for
implementation of the techniques developed in Mathematica.

@@

The R package tourr \citep{tourr} provides numerous types of tours. An
additional function, \texttt{radial\_tour()} has been constructed that
will generate a sequence of projections that will decrease the
coordinates for \(V_m\) to \(\boldsymbol{0}\) and back to the original
values. It is applicable for any projection dimension, \(d\). Changing
slice center manually can be accomplished with the new function,
\texttt{manual\_slice()}. This changes the value of the center point
(\(\mathbf{c}\)) of the slice, along a selected variable axis. It slices
from the center of the data out to one side, back to the center, out to
the opposite side, and then back to the center. The appendix contains a
discussion of a possible visual guide for the slice center location.
